---
title: "RAD LIBRARY PREPARATION SBF1 PROTOCOL"
author: "MS"
date: "12 April 2015"
output:
  html_document:
    theme:
    - spacelab
  pdf_document:
  - default
  word_document:
  - default
---

Protocol based on Fuentes-Utrilla (unpublished), which is based on Etter et al (2011 Methods Mol Biol 772:157-78) and on Baird et al (2008 PloS ONE 3:e3376). Modified
by Kanchon Dasmahapatra. Main difference is using the SBF1 restriction enzyme which
is a low-frequency cutter.

### Overview of the method

* Individual DNA samples are first digested with restriction enzyme SBFI.

* Individually barcoded P1 adapters are ligated to compatible ends of each digested DNA sample.

* The uniquely barcoded samples are then pooled into multiplexed libraries that will consist of a maximum of 16 individual DNA's.

* Each pooled library is sheared to an optimal size of ~ 200-600bp followed by gel size selection. (or Pippin pred)

* Libraries are then blunted, followed by A-tailing and P2 adapter ligation.

* Finally, libraries are enriched, and can be tagged with a second unique barcode during PCR amplification. 


### General advice for Lab-newbies

* Work on ice if possible. Sample and reagents are precious and you don´t want 
them to degrade. If your lab doesn´t provide ice, just work with part of the samples
and have the rest in the fridge / freezer.

* Find a simple system to integrate your excel table with the plates 
and pipettes you are using. For example, when you prepare 8 samples in a column
on the plate, sort your excel table, your pipettes and your samples in the same way,
so you don´t have to think about the next step.

* Look at what the fluid in your pipette is doing! Often filter pipettes don´t suck up
properly because the filter touch the fluid. Or the sample itself is gloupy and that´s why
its not sucked up. So have an eye on the details.

* When preparing a Mastermix, use ~ 5 % more than required. When preparing a Mastermix
for 16 samples, just do it for 17 as you will usually lose a bit of fluid due to pipetting
unreliabilities. Control the rest liquid in you Mastermix after pipetting to check whether
you made any errors.

* Last but not least: stop labwork if you feel that your concentration fades away. Otherwise you
will make errors, believe me.

***

### Summary of the method
 
1.	Pre library sample QC
2.	DNA restriction digest
3.	P1 adapter ligation
4.	DNA shearing
5.	Gel Size selection
6.	Pippen Blue Size Selection
7.	Blunt ends
8.	A-tailing
9.	P2 adapter ligation
10.	Test PCR amplification
11.	Enrichment PCR amplification


***

```{r child = 'sample_qc.Rmd'}
```

***

```{r child = 'DNA_restriction_digest.Rmd'}
```

***

```{r child = 'P1_adapter_ligation.Rmd'}
```

***

```{r child = 'DNA_shearing.Rmd'}
```

***

```{r child = 'Gel_size_selection.Rmd'}
```

***

```{r child = 'Pippin_prep_size_selection.Rmd'}
```









